
%=================================================%
%       REMEMBER TO SORT THE BIBLIOGRAPHY
%=================================================%


\begin{thebibliography}{99}
    
    
    \bibitem[BennVennElectronics, 2018]{BENNVENN2018}
    BennVennElectronics
    \bibYear{2018}
    \bibTitle{GBC Amp Mod}
    [Online video], 27 February 2018. Available from:
    \bibUrl{\url{https://www.youtube.com/watch?v=iyG_c3MIVwI}}
    \bibUrldate{24 October 2019}.
    
    \bibitem[Collins et al., 2014]{COLLINS2014}
    Collins, K. and Kapralos, B. and Tessler, H. and Paul, J. L.
    \bibYear{2014}
    \bibTitle{The Oxford Handbook of Interactive Audio.}
    Oxford: Oxford University Press.
    
    \bibitem[Cunningham, G., 2018]{CUNNINGHAM2018}
    Cunningham, G.
    \bibYear{2018}
    Product Development Stages
    \bibTitle{CUNNINGHAM CONSULTING - Hardware and Software Engineering}, 26 August 2018
    [Online]. Available from:
    \bibUrl{\url{https://www.cunninghamconsulting.net/2018/08/26/product-development/}}
    \bibUrldate{1 November 2019}.
    
    \bibitem[Korg Inc., 2013]{KORG2013}
    Korg Inc.
    \bibYear{2013}
    \bibTitle{KORG Analogue Bass Machine volca bass (volca-bass) - SERVICE MANUAL}
    [Online]. Available from:
    \bibUrl{\url{http://www.ksadhu.niezba.org/sajty/korg_volca_bass_sm.pdf}}
    \bibUrldate{1 November 2019}.
    
    \bibitem[Korg Inc., 2019]{KORG2019}
    Korg Inc.
    \bibYear{2019}
    \bibTitle{Volca Series Lineup}
    [Product page] [Online]. Available from: 
    \bibUrl{\url{https://www.korg-volca.com/en/}}
    \bibUrldate{5 November 2019}.
    
    \bibitem[Kotlinski, J., 2007]{KOTLINSKI2007}
    Kotlinski, J.
    \bibYear{2007}
    \bibTitle{Little Sound Dj v3.7.4 - Operating Manual}
    [Online]. Available from:
    \bibUrl{\url{https://www.littlesounddj.com/lsd/latest/documentation/LSDj_3_7_4.pdf}}
    \bibUrldate{20 September 2019}.
    
    \bibitem[Marquez, 2014]{MARQUEZ2014}
    Marquez, I.
    \bibYear{2014}
    Playing new music with old games: The chiptune subculture.
    \bibTitle{G| A| M| E Games as Art, Media, Entertainment}
    [Online], 1 (3), pp. 67-79. Available from: 
    \bibUrl{\url{http://www.gamejournal.it/wp-content/uploads/2014/04/GAME_3_Subcultures_Journal_Marquez.pdf}}
    \bibUrldate{20 October 2019}.
    
    \bibitem[Nandakumar, M., 2018]{NANDAKUMAR2018}
    Nandakumar, M.
    \bibYear{2018}
    \bibTitle{Using UML - Software Engineering with Objects and Components.}
    2\textsuperscript{nd} ed.
    Edinburgh: Pearson Education Limited.
    
    \bibitem[Nintendo, 2019]{NINTENDO2019}
    Nintendo
    \bibYear{2019}
    \bibTitle{Game Boy, Game Boy Color, Game Boy Pocket Technical Data}
    [Support page] [Online]. Available from: 
    \bibUrl{\url{https://www.nintendo.co.uk/Support/Game-Boy-Pocket-Color/Product-information/Technical-data/Technical-data-619585.html}}
    \bibUrldate{20 October 2019}.
  
    \bibitem[RetroRepairs, 2019]{RETROREPAIRS2019}
    RetroRepairs
    \bibYear{2019}
    \bibTitle{Game Boy DMG - Backlight and Bivert Mod - Fixing eBay Junk}
    [Online video], 15 April 2019. Available from:
    \bibUrl{\url{https://www.youtube.com/watch?v=-nZD3q4i-Cc&t=1026s}}
    \bibUrldate{6 November 2019}.
    
    \bibitem[Stevens, P. and Pooley, R., 2006]{STEVENS2006}
    Stevens, P. and Pooley, R.
    \bibYear{2006}
    \bibTitle{Lean Product Management: Successful products from fuzzy business ideas.}
    Birmingham: Packt Publishing.
    
    \bibitem[TEDx Talks, 2013]{TEDX2013}
    TEDx Talks
    \bibYear{2013}
    \bibTitle{Chiptune: Pushing the Limits Using Constraints: Dan Behrens(Danimal Cannon) at TEDxBuffalo}
    [Online video], 15 November 2013. Available from:
    \bibUrl{\url{https://www.youtube.com/watch?v=_7k25pwNbj8}}
    \bibUrldate{27 October 2019}.
    
    \bibitem[This Does Not Compute, 2016]{THISDOESNOTCOMPUTE2016}
    This Does Not Compute
    \bibYear{2016}
    \bibTitle{Backlight and Bivert Your Original Game Boy DMG!}
    [Online video], 5 January 2016. Available from:
    \bibUrl{\url{https://www.youtube.com/watch?v=xS8NQ3dds2k}}
    \bibUrldate{7 November 2019}.
    
    \bibitem[trash80, 2017]{TRASH802017}
    trash80
    \bibYear{2017}
    \bibTitle{Official ArduinoBoy Repository for serial MIDI communication to the Nintendo Gameboy},
    11 June 2017 [Online]. Available from:
    \bibUrl{\url{https://github.com/trash80/Arduinoboy}}
    \bibUrldate{13 October 2019}.
    
    \bibitem[Trybus, M., 2013]{TRYBUS2013}
    Trybus, M.
    \bibYear{2013}
    HOW TO MAKE A KEYBOARD - THE MATRIX
    \bibTitle{komar's techblog}, 2 September 2013
    [Online]. Available from:
    \bibUrl{\url{http://blog.komar.be/how-to-make-a-keyboard-the-matrix/}}
    \bibUrldate{7 November 2019}.
    
    \bibitem[8BC Chiptune Wiki, 2007]{8BCCHIPTUNE2007}
    8BC Chiptune Wiki
    \bibYear{2007}
    \bibTitle{Game Boy}
    [Online]. Available from: 
    \bibUrl{\url{https://web.archive.org/web/20080221140919/http://8bitcollective.com/wiki/index.php?title=Game_Boy\#Sound}}
    \bibUrldate{5 October 2019}.
    
    \bibitem[8bitjunkie, 2014]{8BITJUNKIE2014}
    8bitjunkie
    \bibYear{2014}
    \bibTitle{How to: Original Game Boy DMG Internal Prosound Mod}
    [Online video], 10 October 2014. Available from:
    \bibUrl{\url{https://www.youtube.com/watch?v=FGlY0quuHGw}}
    \bibUrldate{29 October 2019}.

\end{thebibliography}
